\documentclass[a4paper, 11pt, BCOR = 0 pt, oneside, english]{scrartcl}
\usepackage{tikz}
\usepackage{verbatim}
\usetikzlibrary{arrows, shapes}
\usepackage[light, largesmallcaps]{kpfonts}
\usepackage{coffeestains}
\usepackage[useregional]{datetime2}
\usepackage{gitinfo2}
\usepackage{scrlayer-scrpage}
\clearpairofpagestyles
\usepackage{lastpage}
\usepackage[english]{babel}
\author{Patrick Bideault}
\usepackage{hyperref}
\hypersetup{
	  pdftitle = LaTeX Coffee Stains,
          colorlinks,
	  linkcolor={teal!60!black},
          citecolor={teal!60!black},
          urlcolor={brown!60!black}
        }
% \ifoot{\textsf{HBS / RG 2021 / aerial systems request for quotations / Novafly
%     financial offers
%     \\\textcolor{lightgray}{version \gitRel{} (\gitAbbrevHash{}) -- \DTMdisplaydate{gitdate}}
%   }}
% \cfoot{}
% \ofoot{\thepage/\pageref{LastPage}}
\newpairofpagestyles{titlepage}{
  \ifoot{The command used for the above coffee stain is \verb|\coffeestainA{0.9}{0.85}{-25}{5cm}{1.3cm}|\\\textcolor{lightgray}{version \gitRel{} (\gitAbbrevHash{}) -- \today}}
  \cfoot{}
  \ofoot{\thepage/\pageref{LastPage}}
  }
\newpairofpagestyles{page2}{
  \ifoot{The command used for the above coffee stain is \verb|\coffeestainC{0.6}{1}{180}{0}{0}|\\\textcolor{lightgray}{version \gitRel{} (\gitAbbrevHash{})}}% -- \DTMusedate{gitdate}}}
  \cfoot{}
  \ofoot{\thepage/\pageref{LastPage}}
  }

  \begin{document}
  \pagestyle{titlepage}
\title{LaTeX Coffee Stains}
\author{a package by Hanno Rein\\
  maintained by Patrick Bideault\\
  \texttt{pb-latex@gmx.fr}\\
  ~\\
  \url{https://framagit.org/Pathe/coffeestains}}
%% VERSION NUMBER
% \renewcommand{\today}{May 1, 2021}
\maketitle

\coffeestainA{0.9}{0.85}{-25}{5cm}{1.3cm}

\section{Introduction}
This package provides an essential feature to \LaTeX~that has been missing for
too long. It adds a coffee stain to your documents. A lot of time can be saved
by printing stains directly on the page rather than adding it manually. You can
choose from four different stain types:
\begin{itemize}
  \item[A.] $270^\circ$ circle stain with two tiny splashes 
  \item[B.] $60^\circ$ circle stain 
  \item[C.] two splashes with light colours
  \item[D.] and a colourful twin splash.
\end{itemize}

\section{Usage}
To use the package, simply place the \texttt{coffeestains.sty} file in the directory with all of your 
other \texttt{.tex} files \textit{or} install it properly (consult your distribution's manual). 
Then include the following line in the header of your document:
\begin{verbatim}
\usepackage{coffeestains}
\end{verbatim}
\newpage{}
  \pagestyle{page2}
To place a coffee stain on a page, put one of the following commands in the source code of the relevant page: 
\begin{verbatim}
\coffeestainA{alpha}{scale}{angle}{xoff}{yoff}
\coffeestainB{alpha}{scale}{angle}{xoff}{yoff}
\coffeestainC{alpha}{scale}{angle}{xoff}{yoff}
\coffeestainD{alpha}{scale}{angle}{xoff}{yoff}
\end{verbatim}
\begin{itemize}
\item \texttt{alpha} is the transparency factor $\in [0,1]$;
\item \texttt{scale} is the scale factor, and the standard is \texttt{scale}=1;
\item \texttt{angle} is the angle of the stain, relative to its center. It is in
  degrees $\in [0,360]$;
\item the position relative to the centre of the page is given by x and
  y offsets \texttt{xoff} and \texttt{yoff}. It is advisable to specify
  a measurement unit.
\end{itemize}


\section{Copyright}
You can freely distribute this package as I do not believe in imaginary
property. All stains were self-made, photographed by Hanno Rein, processed with gimp
and traced with Inkscape. Donations should be made in coffee only. My address
is
\begin{quote}
Hanno Rein\\
DAMTP, CMS\\
Wilberforce Road\\
Cambridge CB3 0WA\\
United Kingdom
\end{quote}
See more coffee stains on the next pages.
\coffeestainC{0.6}{1}{180}{0}{0}

\section{Desired improvements}
This package obviously helps, but many stains are still manually added to
documents: latte stains, tea stains, gazpacho stains\dots{} they all should be
printed in the future.

And our efforts shall go beyond the liquid stains: how many documents get their
grease stains manually printed in repair shops? The \LaTeX{} community shall
address this issue and create the adequate tools.

\section{Change Log}
\begin{itemize}
\item April 3, 2009: initial coffee stain by Hanno Rein. In the git repository,
  version is now tagged 0.1.
\item November 23, 2010: \texttt{coffee2.sty}, an improved version that works
  with pdflatex. Thanks to Evan Sultanik! This version is now tagged 0.2.
\item March 24, 2011: \texttt{coffee3}, another improved version that works
  with pdflatex and allows you to scale, rotate and change the transparency of
  any coffee stain. Thanks to Professor Luis Randez! This version is now tagged
  0.3.
\item May 25, 2012: \texttt{coffee4}, an improved version by Adrian Robson, who
  writes: “I find I rarely manage to put my coffee mug down exacly in the middle
  of my papers.  So I have amended coffee3.sty to support off centre coffee
  stains.” This version is now tagged 0.4.
\item May 1, 2021: the \texttt{coffeestains} package on a git
  repository. The rotation of the stains is now relative to the centre of the
  stain itself, not anymore to the centre of the page. Version 0.5.
\end{itemize}

\section{Eternal mottos}

Coffee is great.

\vspace{5mm}

\noindent{}
Coffee will save the world.

\newpage
\vfill{}
This page was intentionally left blank.
\coffeestainD{0.4}{0.5}{90}{0}{0}
\vfill{}
\newpage
\coffeestainB{0.7}{1}{0}{0}{0}
\newpage
\coffeestainA{0.7}{0.75}{2}{0}{0}
Coffee will save the world.

\end{document}
